---
title: "Actor Analysis"
author: "Abel Kassa"
date: "2/12/2020"
output: html_document
---

```{r setup, include = FALSE}
source("analysis.R")
library("knitr")
actor_name <- "Will Smith"
```

This is page analyzes data about movie actors. Enjoy!

## Trending Actors
```{r, include = FALSE}
 date <- Sys.Date() - 7 # Calculating date dynamically
```
Who are the **top** trending count **trending** people on TMDB (week of `r date`)

```{r Trending Table, echo = FALSE}
kable(get_trending_table()) # Rendering table for R markdown using kable()
```

## `r actor_name`

```{r Specific Actor, include = FALSE}
 actor_data <- get_actor_data(actor_name)
  bio <- actor_data$biography
  imdb <- actor_data$imdb_id
  imdb_page <- paste0("https://www.imdb.com/name/",imdb)
  known_for <- actor_data$titles
  film_titles <- paste("-", known_for, collapse = "\n") # Rendering link for R markdown

```
### Favorite Actor
Though they may not be included in that list for some reason, my favorite actor is **`r actor_name`**.

`r imdb_page` They are known for: 

`r film_titles`


Their biography:
`r bio`

### Total Production Credits & The Average Rating For Those Productions

``` {r Actor Analysis, include = FALSE}

data <- analyze_actor()
total_credits <- data$productions
average_rate <- data$average
raw_data <- data$raw

```
Will Smith is known for being in front of the camera but how many TV credits does 
Will Smith have as strictly being a television series producer behind the camera and what was the average
rating of the shows where he received a production credit?

Over the years Will Smith has produced a total of **`r total_credits`** shows! During that period the average rating of the those television productions was **`r average_rate`** out of 10.

```{r Raw Data, echo = FALSE}

kable(raw_data) # Rendering table for markdown using kable() 

```

